### 2015-06-06 chapters/ipa_meets_unicode.tex
adding pitfall multiple options in IPA

\section{Pitfall: Many IPA homoglyphs}
\label{pitfall-there-are-many-ipa-homoglyphs-in-unicode}

@@

@@

\section{Pitfall: No decomposition with some diacritics}
\label{pitfall-no-decomposition-of-overlay}

>>>>

\section{Pitfall: IPA homoglyphs in Unicode}
\label{pitfall-ipa-homoglyphs}

@@

\section{Pitfall: Homoglyphs in IPA}

It is not just the Unicode Standard that offers multiple options for encoding 
the IPA. Even the IPA itself is not consistent in how specific meaningful 
transcriptions have to be encoded. There are a few cases in which the IPA 
explicitly allows for different options of transcribing the same phonetic 
content
\begin{itemize}
  \item tone marks (prefer tone symbols)
  \item marking of <g>
  \item marking of voiceless with ring diacritic
  \item tie bar
\end{itemize}

@@

\section{Pitfall: Missing decomposition}
\label{pitfall-missing-decomposition}
